LME-MPM applied to quasi-brittle fracture.

### 2020-06-30 2020_EFM_MPM_Eigensoftening.tex

\DM{The proposed approach to overcome the two main shortcomings of
  EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``three
  benchmark tests''}.
The first one deals with the presence of stress
instabilities provoked by the spatial discretization, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
approximants are introduced as an alternative to the existing interpolation techniques. Its
performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
notoriously the quality of the results as it is observed in Section
\ref{sec:3.1}, where both interpolation techniques
are compared by carrying out an eigenerosion simulation. The second
limitation is concerned to its inability to simulate properly quasi-brittle
fracture \cite{Navas_2018_ES}. It can be solved through the
eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
of it is exposed in Sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results
are compared \PNA{with numerical ones, being the eigensoftening technique the one employed in this research for the
computations.} In the first case comparing with a semicircular bending
test and in the second case with a drop-weight impact test.}

\subsection{Edge-cracked square panel in mode I}
\label{sec:3.1}
The aim of the problem presented hereinafter is to assess the
capability of the \acrshort{lme} approximants to improve the result
\textit{versus} the standard linear interpolation. The application
consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
control on the outer flanks of the plate (See Figure
\ref{fig:geometry-cracked-panel-mode-I} for details). 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figure-Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The constitutive model considered in the numerical experiment is a
linear-elastic Hookean material, whose Young's modulus \MMP{\gls{E} = 1.06
$[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be tested against experimental results, where
scale factor is relevant, but will be validated against an analytical
solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
\acrshort{mpm}, two different discretizations are required. On the one
hand, a cartesian grid of nodes is considered with a nodal spacing
value of 0.025 $[L]$. On the other hand, the plate will be modeled with a
initial layout of four particles per element and occupying the Gauss
quadrature positions.\\

>>>>

\DM{The proposed approach to overcome the two main shortcomings of
  EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``three
  benchmark tests''}.
The first one deals with the presence of stress
instabilities provoked by the spatial discretisation, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
approximants are introduced as an alternative to the existing interpolation techniques. Its
performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
notoriously the quality of the results as it is observed in Section
\ref{sec:3.1}, where both interpolation techniques
are compared by carrying out an eigenerosion simulation. The second
limitation is concerned to its inability to simulate properly quasi-brittle
fracture \cite{Navas_2018_ES}. It can be solved through the
eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
of it is exposed in Sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results
are compared \PNA{with numerical ones, being the eigensoftening technique the one employed in this research for the
computations.} In the first case comparing with a semicircular bending
test and in the second case with a drop-weight impact test.}

\subsection{Edge-cracked square panel in mode I}
\label{sec:3.1}
The aim of the problem presented hereinafter is to assess the
capability of the \acrshort{lme} approximants to improve the result
\textit{versus} the standard linear interpolation. The application
consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
control on the outer flanks of the plate (See Figure
\ref{fig:geometry-cracked-panel-mode-I} for details). 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{Figure-Mode_I}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-cracked-panel-mode-I}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The constitutive model considered in the numerical experiment is a
linear-elastic Hookean material, whose Young's modulus \MMP{\gls{E} = 1.06
$[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be tested against experimental results, where
scale factor is relevant, but will be validated against an analytical
solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
\acrshort{mpm}, two different discretisation are required. On one
hand, a cartesian grid of nodes is considered with a nodal spacing
value of 0.025 $[L]$. On the other hand, the plate will be modeled with a
initial layout of four particles per element and occupying the Gauss
quadrature positions.\\
